Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-23 ms.tex
Fixing stagnation radius description in text.

If the SMBH dominates the gravitational potential at the stagnation
radius, then $v_{w} \gtrsim \sigma$ and hence the stagnation radius
resides well inside the sphere of influence ($r_{\rm s} < r_{\rm
  soi}$; eq.~[\ref{eq:rsoi}]).  In this limit, equation
(\ref{eq:stag_analytic}) simplifies to
\begin{align}
  &\rs \underset{v_w \gtrsim \sigma}\approx
  \left(\frac{13+8\Gamma}{4+2\Gamma}-\densSlope
    \frac{3}{2+\Gamma}\right)\frac{G \Mbh}{\densSlope v_w^2}
  \approx \begin{cases} 9
    \, \pc \,\, \Mbheight v_{500}^{-2}\, \pyear& \text{core} \\
    4 \, \pc \,\, \Mbheight v_{500}^{-2} \, \pyear & \text{cusp},
  \end{cases}
  \label{eq:stag_simple}
\end{align}
where we have used equation~\eqref{eq:densSlope} to estimate
$\densSlope$: $\densSlope\approx 1$ and $\densSlope \approx 0.6$ for
core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies.  This
expression is similar to that obtained by \citet{Volonteri+11} on more
heuristic grounds (their eq.~6).

In the opposite limit of weak heating ($v_{w} \ll \sigma$), the
stagnation radius moves to large radii $\gg r_{\rm soi}$ or may not
exist at all, formally implying that the entire ISM of the galaxy is
accreting.  This result makes intuitive sense: gas is supplied to the
nuclear by stars which are gravitationally bound to the black hole, so
outflows are possible only if the specific heating rate $\sim
v_{w}^{2}$ significantly exceeds the specific gravitational binding
energy $\sim \sigma^{2}$.  In fact, for core galaxies the specific
heating rate necessary to produce an unbound outflow can greatly
exceed $\sigma^{2}$ due to the additional gravitational potential of
stars outside the sphere of influence (Appendix~\ref{app:be}).

>>>>

If the stagnation radius is well inside the influence radius, $\rsoi$,
then $\Mstar/\Mbh|_{\rs}\ll1$. Also, equation~\eqref{eq:rsRinf}
implies that $v_w\gg \sigma_0$, since
$\rs/\rsoi=\frac{k(\Gamma)}{3\zeta^2}$, where
$\zeta=\sqrt{\frac{v_w^2+\sigma_0^2}{\sigma_0^2}}$ and $k(\Gamma)$ is
of order unity then equation~\eqref{eq:stag_analytic} simplifies to
\begin{align}
  &\rs \underset{v_w \gtrsim \sigma}\approx
  \left(\frac{13+8\Gamma}{4+2\Gamma}-\densSlope
    \frac{3}{2+\Gamma}\right)\frac{G \Mbh}{\densSlope v_w^2}
  \approx \begin{cases} 9
    \, \pc \,\, \Mbheight v_{500}^{-2}\, \pyear& \text{core} \\
    4 \, \pc \,\, \Mbheight v_{500}^{-2} \, \pyear & \text{cusp},
  \end{cases}
  \label{eq:stag_simple}
\end{align}
where we have used equation~\eqref{eq:densSlope} to estimate
$\densSlope$: $\densSlope\approx 1$ and $\densSlope \approx 0.6$ for
core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies.  This
expression is similar to that obtained by \citet{Volonteri+11} on more
heuristic grounds (their eq.~6).

In the opposite limit of weak heating ($v_{w} \ll \sigma_0$),
the stagnation radius moves towards the break radius, $\rb$ in the
stellar density profile, formally implying that almost entire ISM of the galaxy is
accreting.  This result makes intuitive sense: gas is supplied to the
nuclear by stars which are gravitationally bound to the black hole, so
outflows are possible only if the specific heating rate $\sim
v_{w}^{2}$ significantly exceeds the specific gravitational binding
energy.
%   In fact, for core galaxies the specific
% heating rate necessary to produce an unbound outflow can greatly
% exceed $\sigma^{2}$ due to the additional gravitational potential of
% stars outside the sphere of influence (Appendix~\ref{app:be}).
